PANCHANGE_data_preprocessing

### 2020-09-16 PANCHANGE_data_preprocessing2020-07-15.Rmd
deleted the neurological stuff from the PANCHANGE_analysis script
Small edits to pre-processing script made to enable knitting.

```{r mhd restricting_vs_binge_eating_eating_disorders}
if(EDGI == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    restricting_vs_binge_eating_eating_disorders_numeric =
      case_when(
        mhd.anorexia_nervosa_numeric == "1" ~ 1,
        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
        mhd.bulimia_nervosa_numeric == "1" ~ 2,
        mhd.atypical_bulimia_nervosa_numeric == "1" ~ 2, # additional diagnosis in EDGI but not in GLAD
        mhd.bingeeating_disorder_numeric == "1" ~ 2,
        mhd.atypical_bingeeating_disorder_numeric == "1" ~ 2, # additional diagnosis in EDGI
        (mhd.anorexia_nervosa_numeric == "0" &
        mhd.atypical_anorexia_nervosa_numeric == "0" &
          mhd.atypical_anorexia_nervosa_numeric == "0" &
        mhd.bulimia_nervosa_numeric == "0" &
          mhd.atypical_bulimia_nervosa_numeric == "0" &
        mhd.bingeeating_disorder_numeric == "0" &
          mhd.atypical_bingeeating_disorder_numeric == "0") ~ 0
      )
  )

@@

```{r Check eating_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id %>%
  select(
    eating_disorders,
    eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    restricting_vs_binge_eating_eating_disorders_numeric,
    mhd.anorexia_nervosa_numeric,
    mhd.atypical_anorexia_nervosa_numeric,
    mhd.bulimia_nervosa_numeric,
    mhd.bingeeating_disorder_numeric,
    mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa,
    mhd.bingeeating_disorder
  )
}
```

```{r Check eating_disorders}
if(EDGI == TRUE) {
mhd.raw.id %>%
  select(
    eating_disorders,
    eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    restricting_vs_binge_eating_eating_disorders_numeric,
    mhd.anorexia_nervosa_numeric,
    mhd.atypical_anorexia_nervosa_numeric,
    mhd.bulimia_nervosa_numeric,
    mhd.bingeeating_disorder_numeric,
    mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa,
    mhd.atypical_bulimia_nervosa,
    mhd.bingeeating_disorder,
    mhd.atypical_bingeeating_disorder
  )
}
```

@@

```{r mhd check none of the above}
if(RAMP == TRUE) {
mhd.raw.id %>%
  select(
    control,
    mhd.none_of_the_above,
    mhd.none_of_the_above.1
  )

@@

```{r mhd check none of the above}
if(NBR == TRUE | EDGI == TRUE) {
mhd.raw.id %>%
  group_by(control) %>%
  count(
    mhd.none_of_the_above.1,
    mhd.none_of_the_above,
    mhd.other_please_tell_us_more,
    mhd.other_eating_disorder
  )
}
```

@@

```{r mhd categories}
if(EDGI == TRUE) {
mhd.raw.categories <- mhd.raw.id %>%
  select(
    Sample,
    ID,
    anxiety_disorders_numeric,
    anxiety_disorders,
    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
    mhd.specific_phobia_e.g._phobia_of_flying,
    mhd.social_anxiety_or_social_phobia_numeric,
    mhd.social_anxiety_or_social_phobia,
    agoraphobia_panic_disorder_numeric,
    agoraphobia_panic_disorder,
    depressive_disorders_numeric,
    depressive_disorders,
    eating_disorders_numeric,
    eating_disorders,
    obsessive_compulsive_disorders_numeric,
    obsessive_compulsive_disorders,
    psychotic_disorders_numeric,
    psychotic_disorders,
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
    mhd.mania_hypomania_bipolar_or_manicdepression,
    mhd.posttraumatic_stress_disorder_ptsd_numeric,
    mhd.posttraumatic_stress_disorder_ptsd,
    autism_spectrum_disorder_numeric,
    autism_spectrum_disorder,
    mhd.attention_deficit_hyperactivity_disorder_numeric,
    mhd.attention_deficit_hyperactivity_disorder,
    mhd.personality_disorder_numeric,
    mhd.personality_disorder,
#    personality_cluster_a_numeric,
#    personality_cluster_a,
#    personality_cluster_b_numeric,
#    personality_cluster_b,
#    personality_cluster_c_numeric,
#    personality_cluster_c,
    depression_and_anxiety_numeric,
    depression_and_anxiety,
    restricting_vs_binge_eating_eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    bipolar_and_schizophrenia_numeric,
    bipolar_and_schizophrenia,
    control_numeric,
    control,
    disorders_total_count,
    comorbidity_total_count_numeric,
    comorbidity_total_count_factor_numeric,
    comorbidity_total_count_factor
    ) %>%
  add_column(
    personality_cluster_a_numeric = NA_real_,
    personality_cluster_a = NA_character_,
    personality_cluster_b_numeric = NA_real_,
    personality_cluster_b = NA_character_,
    personality_cluster_c_numeric = NA_real_,
    personality_cluster_c = NA_character_
  )
}
```

@@

```{r coping glad gad copy}
if(GLAD == TRUE) {
  coping.phq.raw.id <- coping.glad.phq.raw.id
}
```

@@

```{r coping edgi gad copy}
if(EDGI == TRUE) {
  coping.phq.raw.id <- coping.edgi.phq.raw.id
}
```

@@

```{r coping nbr gad copy}
if(NBR == TRUE) {
  coping.phq.raw.id <- coping.nbr.phq.raw.id
}
```

@@

```{r coping ramp gad copy}
if(RAMP == TRUE) {
  coping.phq.raw.id <- ramp.phq.raw.id
}
```

@@

dim(dat.raw)[1]-dim(dat.no.sex)[1]
}
```
`r dim(dat.glad.raw)[1]-dim(dat.no.sex)[1]` were excluded because they did not report their sex

@@

dim(dat.no.sex.no.gender)[1]-dim(dat.no.sex.no.gender.no.age)[1]
```
`r dim(dat.no.gender)[1]-dim(dat.no.sex.no.gender.no.age)[1]` were excluded because they did not report their age

@@

Proportion of people signed up over half a year ago
```{r glad/edgi ppts signed up over half a year ago, r eval=FALSE, include=FALSE}
if(GLAD == TRUE | EDGI == TRUE){
dat <- dat %>%
  mutate(
    over_half_a_year_time_diff_sign_up_coping_numeric =
      as.numeric(
        if_else(time_diff_sign_up_coping > 182.5, 1, 0
                )
      )
  )

>>>>

```{r EDGI mhd restricting_vs_binge_eating_eating_disorders}
if(EDGI == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    restricting_vs_binge_eating_eating_disorders_numeric =
      case_when(
        mhd.anorexia_nervosa_numeric == "1" ~ 1,
        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
        mhd.bulimia_nervosa_numeric == "1" ~ 2,
        mhd.atypical_bulimia_nervosa_numeric == "1" ~ 2, # additional diagnosis in EDGI but not in GLAD
        mhd.bingeeating_disorder_numeric == "1" ~ 2,
        mhd.atypical_bingeeating_disorder_numeric == "1" ~ 2, # additional diagnosis in EDGI
        (mhd.anorexia_nervosa_numeric == "0" &
        mhd.atypical_anorexia_nervosa_numeric == "0" &
          mhd.atypical_anorexia_nervosa_numeric == "0" &
        mhd.bulimia_nervosa_numeric == "0" &
          mhd.atypical_bulimia_nervosa_numeric == "0" &
        mhd.bingeeating_disorder_numeric == "0" &
          mhd.atypical_bingeeating_disorder_numeric == "0") ~ 0
      )
  )

@@

```{r Check eating_disorders}
if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id %>%
  select(
    eating_disorders,
    eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    restricting_vs_binge_eating_eating_disorders_numeric,
    mhd.anorexia_nervosa_numeric,
    mhd.atypical_anorexia_nervosa_numeric,
    mhd.bulimia_nervosa_numeric,
    mhd.bingeeating_disorder_numeric,
    mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa,
    mhd.bingeeating_disorder
  )
}
```

```{r EDGI Check eating_disorders}
if(EDGI == TRUE) {
mhd.raw.id %>%
  select(
    eating_disorders,
    eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    restricting_vs_binge_eating_eating_disorders_numeric,
    mhd.anorexia_nervosa_numeric,
    mhd.atypical_anorexia_nervosa_numeric,
    mhd.bulimia_nervosa_numeric,
    mhd.bingeeating_disorder_numeric,
    mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa,
    mhd.atypical_bulimia_nervosa,
    mhd.bingeeating_disorder,
    mhd.atypical_bingeeating_disorder
  )
}
```

@@

```{r RAMP mhd check none of the above}
if(RAMP == TRUE) {
mhd.raw.id %>%
  select(
    control,
    mhd.none_of_the_above,
    mhd.none_of_the_above.1
  )

@@

```{r NBR EDGI mhd check none of the above}
if(NBR == TRUE | EDGI == TRUE) {
mhd.raw.id %>%
  group_by(control) %>%
  count(
    mhd.none_of_the_above.1,
    mhd.none_of_the_above,
    mhd.other_please_tell_us_more,
    mhd.other_eating_disorder
  )
}
```

@@

```{r EDGI mhd categories}
if(EDGI == TRUE) {
mhd.raw.categories <- mhd.raw.id %>%
  select(
    Sample,
    ID,
    anxiety_disorders_numeric,
    anxiety_disorders,
    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
    mhd.specific_phobia_e.g._phobia_of_flying,
    mhd.social_anxiety_or_social_phobia_numeric,
    mhd.social_anxiety_or_social_phobia,
    agoraphobia_panic_disorder_numeric,
    agoraphobia_panic_disorder,
    depressive_disorders_numeric,
    depressive_disorders,
    eating_disorders_numeric,
    eating_disorders,
    obsessive_compulsive_disorders_numeric,
    obsessive_compulsive_disorders,
    psychotic_disorders_numeric,
    psychotic_disorders,
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
    mhd.mania_hypomania_bipolar_or_manicdepression,
    mhd.posttraumatic_stress_disorder_ptsd_numeric,
    mhd.posttraumatic_stress_disorder_ptsd,
    autism_spectrum_disorder_numeric,
    autism_spectrum_disorder,
    mhd.attention_deficit_hyperactivity_disorder_numeric,
    mhd.attention_deficit_hyperactivity_disorder,
    mhd.personality_disorder_numeric,
    mhd.personality_disorder,
#    personality_cluster_a_numeric,
#    personality_cluster_a,
#    personality_cluster_b_numeric,
#    personality_cluster_b,
#    personality_cluster_c_numeric,
#    personality_cluster_c,
    depression_and_anxiety_numeric,
    depression_and_anxiety,
    restricting_vs_binge_eating_eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    bipolar_and_schizophrenia_numeric,
    bipolar_and_schizophrenia,
    control_numeric,
    control,
    disorders_total_count,
    comorbidity_total_count_numeric,
    comorbidity_total_count_factor_numeric,
    comorbidity_total_count_factor
    ) %>%
  add_column(
    personality_cluster_a_numeric = NA_real_,
    personality_cluster_a = NA_character_,
    personality_cluster_b_numeric = NA_real_,
    personality_cluster_b = NA_character_,
    personality_cluster_c_numeric = NA_real_,
    personality_cluster_c = NA_character_
  )
}
```

@@

```{r coping glad phq copy}
if(GLAD == TRUE) {
  coping.phq.raw.id <- coping.glad.phq.raw.id
}
```

@@

```{r coping edgi phq copy}
if(EDGI == TRUE) {
  coping.phq.raw.id <- coping.edgi.phq.raw.id
}
```

@@

```{r coping nbr phq copy}
if(NBR == TRUE) {
  coping.phq.raw.id <- coping.nbr.phq.raw.id
}
```

@@

```{r coping ramp phq copy}
if(RAMP == TRUE) {
  coping.phq.raw.id <- ramp.phq.raw.id
}
```

@@

dim(dat.raw)[1]-dim(dat.no.sex)[1]

excluded_no_sex <- dim(dat.raw)[1]-dim(dat.no.sex)[1]

paste("N =", excluded_no_sex, "were excluded because they did not report their sex", sep = " ")
}
```

@@

dim(dat.no.sex.no.gender)[1]-dim(dat.no.sex.no.gender.no.age)[1]

```
`dim(dat.no.sex.no.gender)[1]-dim(dat.no.sex.no.gender.no.age)[1]` were excluded because they did not report their age

@@

Proportion of people signed up over half a year ago
```{r glad/edgi ppts signed up over half a year ago, eval=FALSE, include=FALSE}
if(GLAD == TRUE | EDGI == TRUE){
dat <- dat %>%
  mutate(
    over_half_a_year_time_diff_sign_up_coping_numeric =
      as.numeric(
        if_else(time_diff_sign_up_coping > 182.5, 1, 0
                )
      )
  )
